---
title: |
    **Wasting time on making a BA look beautiful: \
     A RMarkDown Thesis Template**
header-includes:
    - \usepackage{setspace}
    - \doublespacing
classoption:
    - a4paper
bibliography: references.bib
csl: style/apa-style.csl
link-citations: true
output:
    pdf_document:
        fig_caption: yes
        keep_tex: false
        number_sections: true
        toc: false
        toc_depth: 2
        includes:
            in_header: style/preamble.tex
            before_body: style/title.sty
---

\newpage

```{r echo = FALSE, results = FALSE}
print_analysis = TRUE # TRUE or FALSE
print_analysis_results = 'show' # hide or show
```


<!-- Different page numbering for content/formal stuff at the beginning -->
\newpage
\pagenumbering{roman}
\newpage


<!-- Table of contents. Every one of these could be removed -->

\newpage
<!-- Add table of contents -->
\tableofcontents

\newpage
<!-- Add table of contents for figures -->
\listoffigures
\addcontentsline{toc}{section}{List of Figures}

\newpage
<!-- Add table of contents for tables -->
\listoftables
\addcontentsline{toc}{section}{List of Tables}

<!-- start normal page numbering -->
\newpage
\pagenumbering{arabic}
\hypersetup{linkcolor = black}

<!-- I used newpage for major headings/sections -->
\newpage

# Preface {-}

```{r child = 'content/01_preface.Rmd'}
```

\newpage

# Introduction

```{r child = 'content/02_introduction.Rmd'}
```

\newpage

# Theory

```{r child = 'content/03_theory.Rmd'}
```

\newpage

# Methodology

```{r child = 'content/04_methodology.Rmd'}
```

\newpage

# Results

```{r child = 'content/05_results.Rmd'}
```

\newpage

# Discussion

```{r child = 'content/06_discussion.Rmd'}
```

\newpage

# References {-}

<!-- Custom formatting I liked for the references. Basically indents every line except the first a bit. This way, if you look through the references, it is easier to read the author's names. -->
\begingroup
\setlength{\parindent}{-0.4in}
\setlength{\leftskip}{0.4in}
\setlength{\parskip}{8pt}
\noindent

<div id="refs"></div>
\endgroup

\newpage

# Appendix A\label{app1} {-} 

```{r child = 'content/08_Appendix1.Rmd'}
```

\newpage

# Appendix B\label{app2} {-}

```{r child = 'content/09_Appendix2.Rmd'}
```

